Secure Composition of Robust and Optimising Compilers

### 2023-06-13 popl/main.tex
Use the other intro. Change \MKin macro. Add note.

\BrText{Solution}{
This paper introduces a formal framework for secure compiler compositions and showcases the framework's power by instantiating it on a multi-level compilation chain.
To this end, we discuss security property compositions and define several secure compilers, where each is either robustly preserving a different security property of interest or optimizing, i.e., applying \gls{cf} or doing \gls{dce}.
We compose these secure compilers into a multi-level compilation chain which is optimizing and robustly preserves a combination of \gls{ms} and \gls{cct}.
Crucially, the robust preservation proofs are only done for the individual compilers in the compilation chain and the robust preservation for the whole chain is a result of one of our key theorems.
The key results are formalized in Coq.}

% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time. 
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}

>>>>

\BrText{Solution}{
% keyword: pass
\MPin{
	commands missing
}
This paper introduces a framework for reasoning about the composition of secure and optimising compiler passes and it showcases the power of this framework by instantiating it on a multi-pass compilation chain.
To this end, this paper first discusses how to compose security properties, such as temporal and spatial memory safety into general memory safety, and cryptographic constant time.
Then, this paper defines several secure compiler passes, where each is either preserving a different security property (e.g., temporal or spatial memory safety) or performing a security-preserving optimisation, (e.g., applying constant-folding or dead-code elimination).
% keyword- end to end, composition
Finally, this paper shows how to compose these secure compiler passes into a multi-pass compilation chain which can be proven to provide end-to-end preservation of general memory safety and cryptographic constant time.
\MKin{
  ,,can be proven'' -> we prove (?)
}
Crucially, this end-to-end security preservation is obtained by having each compilation pass (i) preserve a sub-part of the overall security property individually and then (ii) compose each preserved security property as dictated by our framework.
Our results showcase how our framework allows the kind of formal security reasoning that compiler writers already want (and do), obtaining precise, compositional security reasoning while providing minimal (and modular) proof effort.
\MPin{
	last line: not the best.
}
}
